\documentclass[11pt,oneside,paper=5.5in:8.5in,DIV=13,chapterprefix=false,headings=big]{scrbook}

\usepackage{microtype}
\usepackage{hyperref}

\usepackage{fvextra}
\DefineVerbatimEnvironment{verbatim}{Verbatim}{fontsize=\small}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}

\addtokomafont{disposition}{\rmfamily}
\RedeclareSectionCommand[
  beforeskip=0pt,
  afterskip=\baselineskip
]{chapter}

\begin{document}

\frontmatter
\begin{center}
\vspace*{2em}
{\Huge\bfseries The Kid Computer}\\
\vspace{0.5em}
{\Large Christmas 2025}\\
\vspace{0.5em}
Sally \& Penny Utterback
\end{center}
\thispagestyle{empty}
\cleardoublepage

\tableofcontents

\mainmatter
\chapter{Welcome}

This is a computer for doing a few things carefully.

You can make pictures.
You can move a turtle.
You can type small programs.

When you are done with something,
you can always come back.

\chapter{The Menu}

When the computer turns on, you see the menu.

The menu lets you choose what to do.

Use the arrow keys to pick what you want.
Press Enter to start it.

To leave and go back to the menu,
hold down Ctrl and Alt,
then press Backspace.

\chapter{The Turtle (Logo): Telling the Computer to Draw}

Instead of drawing yourself, you can tell the computer what to draw,
so that it happpens exactly like you want.

The turtle listens to words.

Try typing:

\begin{verbatim}
FD 50
RT 90
LT 90
\end{verbatim}

You can tell the turtle to move.
You can tell it to turn.

\section{Square}

\begin{verbatim}
FD 100
RT 90
FD 100
RT 90
FD 100
RT 90
FD 100
RT 90
\end{verbatim}

That is a lot of typing.
You can also say:

\begin{verbatim}
REPEAT 4 [FD 100 RT 90]
\end{verbatim}

Try changing:
\begin{itemize}
\item \texttt{100} to make it bigger or smaller
\item \texttt{90} to see what happens
\end{itemize}

\section{Triangle}

\begin{verbatim}
REPEAT 3 [FD 100 RT 120]
\end{verbatim}

\section{Spiral}

\begin{verbatim}
REPEAT 36 [FD 10 RT 10]
\end{verbatim}

Try:
\begin{itemize}
\item changing the numbers
\item making it repeat more times
\end{itemize}

\section{Star}

\begin{verbatim}
REPEAT 5 [FD 100 RT 144]
\end{verbatim}

\section{Flower}

\begin{verbatim}
REPEAT 8 [REPEAT 4 [FD 50 RT 90] RT 45]
\end{verbatim}

\section{Useful Commands}

\begin{itemize}
\item \texttt{CS} — clear the screen
\item \texttt{HOME} — send the turtle back to the middle
\item \texttt{PU} — pen up (move without drawing)
\item \texttt{PD} — pen down (draw again)
\end{itemize}

\chapter{BASIC: Telling the Computer What to Do}

You can do Daddy's job! This computer can run small programs.

Programs are made from lines with numbers.

You type the lines.
Then you type:

\begin{center}
\texttt{RUN}
\end{center}

\section{Useful Commands}

\begin{itemize}
\item \texttt{RUN} — makes the program go
\item \texttt{LIST} — shows what you typed
\item \texttt{NEW} — erase and start over
\item \texttt{CLS} — clear the screen
\end{itemize}

If the screen fills up or will not stop,
press \textbf{Ctrl + C}.

\section{Growing Stars}

This makes stars grow down the screen.

\begin{verbatim}
10 CLS
20 FOR I = 1 TO 20
30 PRINT STRING$(I, "*")
40 NEXT I
50 END
\end{verbatim}

Try changing:
\begin{itemize}
\item \texttt{20} to a bigger number
\item \texttt{"*"} to another letter
\end{itemize}

\section{Letter Rain}

Letters fall forever!

\begin{verbatim}
10 CLS
20 PRINT CHR$(65 + RND * 26);
30 GOTO 20
\end{verbatim}

To stop it, press \textbf{Ctrl + C}.

\section{Bouncing Word}

The word moves back and forth.

\begin{verbatim}
10 CLS
20 FOR X = 1 TO 20
30 PRINT SPC(X) + "HI!"
40 NEXT X
50 FOR X = 20 TO 1 STEP -1
60 PRINT SPC(X) + "HI!"
70 NEXT X
80 GOTO 10
\end{verbatim}

Try changing:
\begin{itemize}
\item \texttt{"HI!"} to your name
\item the numbers to make it move more
\end{itemize}

\section{Number Explosion}

Numbers fill the screen.

\begin{verbatim}
10 CLS
20 FOR I = 1 TO 10
30 PRINT I; I; I; I; I
40 NEXT I
50 END
\end{verbatim}

Try:
\begin{itemize}
\item printing more numbers
\item changing \texttt{I} to \texttt{I * I}
\end{itemize}

\section{Checkerboard}

This makes a pattern.

\begin{verbatim}
10 CLS
20 FOR R = 1 TO 10
30 PRINT "* * * * * "
40 PRINT " * * * * *"
50 NEXT R
60 END
\end{verbatim}

Try:
\begin{itemize}
\item changing the symbols
\item adding more rows
\end{itemize}

\section{Name Shout}

The computer asks your name!

\begin{verbatim}
10 CLS
20 INPUT "WHAT IS YOUR NAME"; N$
30 FOR I = 1 TO 10
40 PRINT N$
50 NEXT I
60 END
\end{verbatim}

Try:
\begin{itemize}
\item changing how many times it prints
\item printing something else
\end{itemize}

%% \clearpage
%% \thispagestyle{empty}
%% \null
% Repeat until page count is a multiple of 4.


\end{document}
